---
title: "IBSC School Dashboard"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    social: menu
    vertical_layout: fill
runtime: shiny
resource_files:
- assets/d3.min.js
- assets/forcedirected/binding.js
- assets/forcedirected/fd.js
- assets/forcedirected/repeated-fd.js
- assets/forcedirected/styles.css
---

```{r setup, include=FALSE}
#on first pull, install any uninstalled packages in packageSetup.R
source("packageSetup.R")

#on first pull, move the .xlsx sheets into the directory, rename them in the
#format "*.Student<class name>.xlsx" and run SchoolDataPrep.R to generate the
#.RDS files in the working directory needed by the dash.  This file need not be
#deployed to increase speed and safeguard alghorithms.

#Read in all .RDS files in the working directory
files = list.files(path = '.', pattern = '^.*rds$')
fileList <- list()
for (i in 1:length(files)) {
  file <- readRDS(files[i])
  name <- as.character(files[i])
  fileList[[name]] <- file
}

set.seed (fileList[[1]]$seed)

#convenience function to find out if a graph is fragmented.
graphConnected <- function(graph) {
  CD <- component_distribution(graph)
  if(length(CD[!CD==0])>1) {
    connected <- FALSE
  } else {
    connected <- TRUE
  }
}

#Convenience wrapper for raw data with download options
create_dt <- function(x){
  DT::datatable(x,
                extensions = 'Buttons',
                options = list(dom = 'Blfrti',
                               buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                               lengthMenu = list(c(50,100, 200, -1),
                                                 c(50, 100, 200, "All")),
                               paginate = TRUE
                               )
               )
}

# make a colour palette
  listOfColours <- c("#9E0142", "#66c2a5", "#C99f47","#D55E00", "#0072B2",
                     "#332288", "#661100")
# make it d3 compatible
  colors <- paste(sapply(listOfColours, function(x) {
    paste0("d3.rgb(",paste(c(col2rgb(x), 0.5),
                           collapse = "," ),
           ")") }),
    collapse = ", ")
  colorJS <- paste0('d3.scaleOrdinal([', colors, '])')
  

#Prep the data for the D3 maps
  
collateData <- function(file, number) {
  nodes <- file$D3NodesList[[number]]
  edges <- file$edgeDataList[[number]]
  t <- list(nodes = nodes, edges = edges)
}

prepData <- function(fileSet, index) {
  First <- collateData(fileSet, number = index)
  #Second <- collateData(fileSet, number = (index+1))
  JSONOut <- list(First = First)
  #JSONOut <- list(First = First, Second = Second)
}

#run d3 prep for all classes in the organisation
for(i in 1:length(fileList)) {
  #run d3 prep for all relationship questions in each class
  for (j in 1:length(fileList[[i]]$D3NodesList)) {
    fileName <- paste("D3JSData",j, i, ".json", sep = "")
    D3JSData <- prepData(fileSet = fileList[[i]], index = j)
    D3JSData <- jsonlite::toJSON(D3JSData)
    write(D3JSData, fileName)
  }
}

#source the D3 code to link the R to JS
source("assets/forcedirected/forcedirected.R")


```


Student - Student Interaction Positivity {data-navmenu="Class Name"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### Question Statement: This person and I have frequent positive interactions either in class or outside class

```{r}
valueBox(
  "Positivity",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[1]]$className,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}
valueBox(
  fileList[[1]]$overallHealth[[1]][[1]],
  color = fileList[[1]]$overallHealth[[1]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[1]]$overallPfI[[1]][[1]],
  color = fileList[[1]]$overallPfI[[1]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[1]]$clientName`.

  Our analysis shows this class to be moderately healthy and with a moderate potential for improvement.

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[1]][[1]] > 0)) {
  cat(fileList[[1]]$homophylyList[[1]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[1]][[3]] > 0)) {
  cat(fileList[[1]]$homophylyList[[1]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[1]][[2]] > 0)) {
  cat(fileList[[1]]$homophylyList[[1]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter

```{r}
diameter <- fileList[[1]]$totalNetworkInfo[[1]][[4]]
nodes <- length(fileList[[1]]$totalNetworkInfo[[1]][[10]])

# derive sector colours for gauge from nrow(nodes) and whether
# the graph is fragmented

if(graphConnected(fileList[[1]]$SSNQGraph[[1]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[1]]$SSNQGraph[[1]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships

```{r}
edgeDensity <- fileList[[1]]$totalNetworkInfo[[1]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity
  
```{r}
reciprocity <- fileList[[1]]$totalNetworkInfo[[1]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=400} 
<center>
```{r}

fileList[[1]]$dendrogramList[[1]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.
  

Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}

JSData1 <- jsonlite::read_json("D3JSData11.json")

repeatedforcedirectedOutput("repeatedforcedirected1")
output$repeatedforcedirected1 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSData1))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.

Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$HSList[[1]]) > 0) {
  cat(fileList[[1]]$HSList[[1]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[1]]$ASList[[1]]) > 0)) {
  cat(fileList[[1]]$ASList[[1]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[1]][[9]][1,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[1]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[1]][[9]][2,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[1]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[1]][[9]][3,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[1]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[1]]$isolatesList[[1]])) {
  cat(fileList[[1]]$isolatesList[[1]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.

Student - Student Knowing One Another {data-navmenu="Class Name"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### Question Statement: I am confident that this person and I know each other's skills and interests

```{r}
valueBox(
  "Knowing",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```


### {-}

```{r}
valueBox(
  fileList[[1]]$className,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}
valueBox(
  fileList[[1]]$overallHealth[[2]][[1]],
  color = fileList[[1]]$overallHealth[[2]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[1]]$overallPfI[[2]][[1]],
  color = fileList[[1]]$overallPfI[[2]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[1]]$clientName`.

  Our analysis shows this class to be moderately healthy and with a moderate potential for improvement.
  
### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[2]][[1]] > 0)) {
  cat(fileList[[1]]$homophylyList[[2]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class


### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[2]][[3]] > 0)) {
  cat(fileList[[1]]$homophylyList[[2]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[2]][[2]] > 0)) {
  cat(fileList[[1]]$homophylyList[[2]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class
  
Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter

```{r}
diameter <- fileList[[1]]$totalNetworkInfo[[2]][[4]]
nodes <- length(fileList[[1]]$totalNetworkInfo[[2]][[10]])

# derive sector colours for gauge from nrow(nodes) and whether
# the graph is fragmented

if(graphConnected(fileList[[1]]$SSNQGraph[[2]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[1]]$SSNQGraph[[2]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships

```{r}
edgeDensity <- fileList[[1]]$totalNetworkInfo[[2]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity
  
```{r}
reciprocity <- fileList[[1]]$totalNetworkInfo[[2]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=400} 
<center>
```{r}

fileList[[1]]$dendrogramList[[2]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.

Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}

JSData2 <- jsonlite::read_json("D3JSData21.json")

repeatedforcedirectedOutput("repeatedforcedirected2")
output$repeatedforcedirected2 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSData2))

```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.

Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$HSList[[2]]) > 0) {
  cat(fileList[[1]]$HSList[[2]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[1]]$ASList[[2]]) > 0)) {
  cat(fileList[[1]]$ASList[[2]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[2]][[9]][1,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[2]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[2]][[9]][2,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[2]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[2]][[9]][3,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[2]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[1]]$isolatesList[[2]])) {
  cat(fileList[[1]]$isolatesList[[2]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.


Student - Student Value and Respect {data-navmenu="Class Name"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### Question Statement: I feel that this person values and respects my contributions in class

```{r}
valueBox(
  "Valuing",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```


### {-}

```{r}
valueBox(
  fileList[[1]]$className,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}
valueBox(
  fileList[[1]]$overallHealth[[3]][[1]],
  color = fileList[[1]]$overallHealth[[3]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[1]]$overallPfI[[3]][[1]],
  color = fileList[[1]]$overallPfI[[3]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[1]]$clientName`.

  Our analysis shows this class to be moderately healthy and with a moderate potential for improvement.
  

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[3]][[1]] > 0)) {
  cat(fileList[[1]]$homophylyList[[3]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[3]][[3]] > 0)) {
  cat(fileList[[1]]$homophylyList[[3]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[3]][[2]] > 0)) {
  cat(fileList[[1]]$homophylyList[[3]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class
  

  
Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter {data-height=150} 

```{r}
diameter <- fileList[[1]]$totalNetworkInfo[[3]][[4]]
nodes <- length(fileList[[1]]$totalNetworkInfo[[3]][[10]])

# derive sector colours for gauge from nrow(nodes) and whether
# the graph is fragmented

if(graphConnected(fileList[[1]]$SSNQGraph[[3]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[1]]$SSNQGraph[[3]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships {data-height=150} 

```{r}
edgeDensity <- fileList[[1]]$totalNetworkInfo[[3]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity {data-height=150} 
  
```{r}
reciprocity <- fileList[[1]]$totalNetworkInfo[[3]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=550} 
<center>
```{r}

fileList[[1]]$dendrogramList[[3]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.


Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}

JSData3 <- jsonlite::read_json("D3JSData31.json")

repeatedforcedirectedOutput("repeatedforcedirected3")
output$repeatedforcedirected3 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSData3))

```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.


Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$HSList[[3]]) > 0) {
  cat(fileList[[1]]$HSList[[3]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[1]]$ASList[[3]]) > 0)) {
  cat(fileList[[1]]$ASList[[3]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[3]][[9]][1,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[3]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[3]][[9]][2,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[3]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[3]][[9]][3,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[3]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[1]]$isolatesList[[3]])) {
  cat(fileList[[1]]$isolatesList[[3]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.



Student - Student Individual Score Profiles {data-navmenu="Class Name"}
=======================================================================

Individual Score Profiles {data-width=900 .tabset}
-----------------------------------------------------------------------

### Interaction Positivity

```{r}
renderPlotly ({
  fileList[[1]]$polarGraphList[[1]]
})
```

> Scores for each person for how well they report knowing one another can be explored here.  Click on the person's name in the list to visualise the scores and hover over the graph for more details.  Select multiple people to overlay their scores for comparison.  The green dotted line is the average score given by the network.


### Knowing One Another

```{r}
renderPlotly ({
  fileList[[1]]$polarGraphList[[2]]
})
```

> Scores for each person for how well they report knowing one another can be explored here.  Click on the person's name in the list to visualise the scores and hover over the graph for more details.  Select multiple people to overlay their scores for comparison.  The green dotted line is the average score given by the network.


### Student Value and Respect

```{r}
renderPlotly ({
  fileList[[1]]$polarGraphList[[3]]
})
```

> Scores for each person for how well they report knowing one another can be explored here.  Click on the person's name in the list to visualise the scores and hover over the graph for more details.  Select multiple people to overlay their scores for comparison.  The green dotted line is the average score given by the network.


Degree {.tabset}
-----------------------------------------------------------------------

### Interaction Positivity

#### 'Interaction Positivity' Degree All Scores

```{r}
renderPlotly ({
  fileList[[1]]$degreeAllHistogramList[[1]]
})
```

> The higher the overall degree score, the more tied in the person is to the class.  Those learners who score nearest the average are those who are best placed to develop resiliency in the relational network of the class when they are encouraged to relate to one another, because they have connections to bring to bear, and have relational overhead to be able to develop further relationships without others suffering from divided attention.

#### 'Interaction Positivity' Degree In Scores

```{r}
renderPlotly ({
  fileList[[1]]$degreeInHistogramList[[1]]
})
```

> A higher 'Degree in' score indicates that more people in the class come
to this person for information

#### 'Interaction Positivity' Degree Out Scores

```{r}
renderPlotly({
  fileList[[1]]$degreeOutHistogramList[[1]]
})
```

> A higher 'Degree out' score indicates that the person is well connected within the class.

### Knowing One Another

#### 'Knowing One Another' Degree All Scores

```{r}
renderPlotly ({
  fileList[[1]]$degreeAllHistogramList[[2]]
})
```

> The higher the overall degree score, the more tied in the person is to the class.  Those learners who score nearest the average are those who are best placed to develop resiliency in the relational network of the class when they are encouraged to relate to one another, because they have connections to bring to bear, and have relational overhead to be able to develop further relationships without others suffering from divided attention.

#### 'Knowing One Another' Degree In Scores

```{r}
renderPlotly ({
  fileList[[1]]$degreeInHistogramList[[2]]
})
```

> A higher 'Degree in' score indicates that more people in the class come
to this person for information

#### 'Knowing One Another' Degree Out Scores

```{r}
renderPlotly({
  fileList[[1]]$degreeOutHistogramList[[2]]
})
```

> A higher 'Degree out' score indicates that the person is well connected within the class.

### Student Value and Respect

#### 'Value and Respect' Degree All Scores

```{r}
renderPlotly ({
  fileList[[1]]$degreeAllHistogramList[[3]]
})
```

> The higher the overall degree score, the more tied in the person is to the class.  Those learners who score nearest the average are those who are best placed to develop resiliency in the relational network of the class when they are encouraged to relate to one another, because they have connections to bring to bear, and have relational overhead to be able to develop further relationships without others suffering from divided attention.

#### 'Value and Respect' Degree In Scores

```{r}
renderPlotly ({
  fileList[[1]]$degreeInHistogramList[[3]]
})
```

> A higher 'Degree in' score indicates that more people in the class come
to this person for information

#### 'Value and Respect' Degree Out Scores

```{r}
renderPlotly({
  fileList[[1]]$degreeOutHistogramList[[3]]
})
```

> A higher 'Degree out' score indicates that the person is well connected within the class

Raw Data {data-navmenu="Class Name"}
=======================================================================

Below is the raw data from which the Relationships Foundation have derived their
analysis. These data are not anonymised and should be treated sensitively.

Student-Student {.tabset}
-----------------------------------------------------------------------

### Student Characteristic Information

```{r}
create_dt(fileList[[1]]$nodes)
```

### Student - Student Interaction Positivity

```{r}
create_dt(fileList[[1]]$rawEdgesList[[1]])
```

### Student - Student Knowing One Another

```{r}
create_dt(fileList[[1]]$rawEdgesList[[2]])
```

### Student - Student Value and Respect

```{r}
create_dt(fileList[[1]]$rawEdgesList[[3]])
```