---
title: "IBSC Dash"
output:
  flexdashboard::flex_dashboard:
    orientation: columns
    social: menu
    vertical_layout: fill
runtime: shiny
resource_files:
- assets/d3.min.js
- assets/forcedirected/binding.js
- assets/forcedirected/fd.js
- assets/forcedirected/repeated-fd.js
- assets/forcedirected/styles.css
---
```{r setup, include=FALSE}

#install and call all relevant libraries
packages = c('rmarkdown', 'jsonlite', 'tidyverse', 'flexdashboard', 'plotly')
invisible(lapply(packages, library, character.only = TRUE))

#read in all files
files = list.files(path = paste(".", "data", sep = "/"), pattern = '^.*rds$')
fileList <- list()
for (i in 1:length(files)) {
  file <- readRDS(paste("./data", files[i], sep = "/"))
  name <- as.character(files[i])
  fileList[[name]] <- file
}

#source all .R scripts in ./assets/R/
file.sources = list.files(path = "./assets/R/", pattern="*.R$")
file.sources <- sapply(file.sources,function(x){paste("./assets/R/", x, sep = "")})
for(i in 1:length(file.sources)){
  source(file.sources[[i]])
}

#source forceDirected.R
source("./assets/forcedirected/forcedirected.R")

#set an arbitary seed
set.seed (fileList[[1]]$seed)


d3ClassOverviewPrepSingleInstance(fileList=fileList)
d3RQPrepSingleInstance(fileList=fileList)
d3ClassOverviewPrepSingleInstance(fileList=fileList)
d3RQPrepSingleInstance(fileList=fileList)
d3ClassOverviewPrepSingleInstance(fileList=fileList)
d3RQPrepSingleInstance(fileList=fileList)
d3ClassOverviewPrepSingleInstance(fileList=fileList)
d3RQPrepSingleInstance(fileList=fileList)
'dupnlmffjcatgle'
```


School Overview {data-orientation=rows}
=======================================================================

Input {.sidebar}
--------------------------------------------------------

```{R}
#build summary data frame
summaryDataFrame <- data.frame()
summaryDataFrameColumnNames <- c("Class Name", "Health", "Reciprocity",
                                 "PfI", "Diameter",
                                 "Density", "Isolates")
for (k in summaryDataFrameColumnNames) {
  summaryDataFrame[[k]] <- as.character()
} 
for (i in 1:length(fileList)) {
  file <- fileList[i]
  summary <- list(file[[1]]$className,
                        file[[1]]$overallScoresList[[length(file[[1]]$overallScoresList)]][[1]],
                        file[[1]]$totalNetworkInfo[[length(file[[1]]$totalNetworkInfo)]][[6]], 
                        file[[1]]$overallScoresList[[length(file[[1]]$overallScoresList)]][[2]], 
                        file[[1]]$totalNetworkInfo[[length(file[[1]]$totalNetworkInfo)]][[4]],
                        file[[1]]$totalNetworkInfo[[length(file[[1]]$totalNetworkInfo)]][[5]], 
                        as.numeric(length(file[[1]]$isolatesSSNQFormatted)))
  summaryDataFrame[i,] <- summary
}

for(i in 2:ncol(summaryDataFrame)){
summaryDataFrame[,i] <- round(as.numeric(summaryDataFrame[,i]), digits = 1)
}

#add an arbitrary score for the x axis of summary graphs
summaryDataFrame$Score <- "A"

classChoices <- summaryDataFrame$'Class Name'

#function to determine scale of whisker plots
scaleFUN <- function(x) sprintf("%.2f", x)

#choose a set of colours equally spaced on the colour wheel
ColourPicker <- function(n) {
  hues = seq(15, 375, length = n + 1)
  hcl(h = hues, l = 65, c = 100)[1:n]
}

#add colours to cases for the whisker plots
summaryDataFrame$color <- ColourPicker(nrow(summaryDataFrame))

```

```{R}
div(style = "margin-top: 1.5vh;")

#create input UI for the whisker plots
selectInput(
  inputId = "Set",
  label = "Class",
  choices = classChoices,
  multiple = T
)

div(style = "margin-top: 27.5vh;")
```

Summary Data {data-height=350}
--------------------------------------------------------

### Class Relational Health

```{r}

output$NetworkHealth <- renderPlot({
  ggplot(summaryDataFrame, aes(x=Score, y=Health)) +
  scale_x_discrete() +
  scale_y_continuous(labels=scaleFUN, limits=c(40,150)) +
  geom_rect(data = summaryDataFrame, aes(),
                                        xmin = -Inf,
                                        xmax = Inf,
                                        ymin = 0,
                                        ymax = 60,
                                        fill = "Red",
                                        alpha = 0.1) +
  geom_rect(data = summaryDataFrame, aes(),
                                        xmin = -Inf,
                                        xmax = Inf,
                                        ymin = 61,
                                        ymax = 100,
                                        fill = "Orange",
                                        alpha = 0.1) +
  geom_rect(data = summaryDataFrame, aes(),
                                        xmin = -Inf,
                                        xmax = Inf,
                                        ymin = 101,
                                        ymax = 150,
                                        fill = "Green",
                                        alpha = 0.1) +
  geom_boxplot(width = 0.25, fill="grey", color="darkslategrey", size = 1) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=60, binwidth = 1/30) +
  geom_point(
    data=subset(summaryDataFrame, summaryDataFrame[[1]] %in% input$Set),
    aes(x=Score, y=Health), 
    size=5, color=
      subset(summaryDataFrame, summaryDataFrame[[1]] %in% input$Set)$color,
      alpha = 0.7) +
  labs(x="", y="") +
   theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.title = element_text(hjust = 0.5))

})

plotOutput("NetworkHealth")
```

### Potential for Improvement


```{r}

output$PfIPlot <- renderPlot({
  ggplot(summaryDataFrame, aes(x=Score, y=PfI)) +
  scale_x_discrete() +
  scale_y_continuous(labels=scaleFUN, limits= c(40, 150)) +
  geom_rect(data = summaryDataFrame, aes(),
                                        xmin = -Inf,
                                        xmax = Inf,
                                        ymin = 0,
                                        ymax = 60,
                                        fill = "Red",
                                        alpha = 0.1) +
  geom_rect(data = summaryDataFrame, aes(),
                                        xmin = -Inf,
                                        xmax = Inf,
                                        ymin = 61,
                                        ymax = 100,
                                        fill = "Orange",
                                        alpha = 0.1) +
  geom_rect(data = summaryDataFrame, aes(),
                                        xmin = -Inf,
                                        xmax = Inf,
                                        ymin = 100,
                                        ymax = 150,
                                        fill = "Green",
                                        alpha = 0.1) +
  geom_boxplot(width = 0.25, fill="grey", color="darkslategrey", size = 1) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=60, binwidth = 1/30) +
  geom_point(
    data=subset(summaryDataFrame, summaryDataFrame[[1]] %in% input$Set),
    aes(x=Score, y=PfI), 
    size=5, color=
      subset(summaryDataFrame, summaryDataFrame[[1]] %in% input$Set)$color,
      alpha = 0.7) +
  labs(x="", y="") +
   theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.title = element_text(hjust = 0.5))
})

plotOutput("PfIPlot")
```

### Reciprocity

```{r}
output$ReciprocityPlot <- renderPlot({
  ggplot(summaryDataFrame, aes(x=Score, y=Reciprocity)) +
  scale_x_discrete() +
  scale_y_continuous(labels=scaleFUN, limits=c(0,1)) +
  geom_boxplot(width = 0.25, fill="grey", color="darkslategrey", size = 1) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.6, binwidth = 1/30) +
  geom_point(
    data=subset(summaryDataFrame, summaryDataFrame[[1]] %in% input$Set),
    aes(x=Score, y=Reciprocity),
    size=5, color=
      subset(summaryDataFrame, summaryDataFrame[[1]] %in% input$Set)$color,
      alpha = 0.7) +
  labs(x="", y="") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.title = element_text(hjust = 0.5))
})

plotOutput("ReciprocityPlot")
```

### Diameter

```{r}
output$DiameterPlot <- renderPlot({
  ggplot(summaryDataFrame, aes(x=Score, y=Diameter)) +
  scale_x_discrete() +
  scale_y_reverse(labels=scaleFUN, limits = c(10,0)) +
  geom_boxplot(width = 0.25, fill="grey", color="darkslategrey", size = 1) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.6, binwidth = 1/3) +
  geom_point(
    data=subset(summaryDataFrame, summaryDataFrame[[1]] %in% input$Set),
    aes(x=Score, y=Diameter), 
    size=5, color=
      subset(summaryDataFrame, summaryDataFrame[[1]] %in% input$Set)$color,
      alpha = 0.7) +
  labs(x="", y="") +
   theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.title = element_text(hjust = 0.5))
})

plotOutput("DiameterPlot")
```

### Edge Density

```{r}
output$DensityPlot <- renderPlot({
  ggplot(summaryDataFrame, aes(x=Score, y=Density)) +
  scale_y_continuous(labels=scaleFUN, limits=c(0,1)) +
  scale_x_discrete() +
  geom_boxplot(width = 0.25, fill="grey", color="darkslategrey", size = 1) +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.6, binwidth = 1/30) +
  geom_point(
    data=subset(summaryDataFrame, summaryDataFrame[[1]] %in% input$Set),
    aes(x=Score, y=Density), 
    size=5, color=
      subset(summaryDataFrame, summaryDataFrame[[1]] %in% input$Set)$color,
      alpha = 0.7) +
  labs(x="", y="") +
   theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        plot.title = element_text(hjust = 0.5))
})

plotOutput("DensityPlot")
```


Scots 7TGAN1 Class Summary {data-navmenu="Scots 7TGAN1"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### These findings are an amalgamation of each peer-to-peer question asked of the learners.

```{r}
valueBox(
  "Overall",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[1]]$`Scots 7TGAN1`,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}
valueBox(
  fileList[[1]]$overallHealth[[length(fileList[[1]]$overallHealth)]][[1]],
  color = fileList[[1]]$overallHealth[[length(fileList[[1]]$overallHealth)]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[1]]$overallPfI[[length(fileList[[1]]$overallHealth)]][[1]],
  color = fileList[[1]]$overallPfI[[length(fileList[[1]]$overallHealth)]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[1]]$clientName`.

  Our analysis shows this class to be moderately healthy and with a moderate potential for improvement.
  

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[length(fileList[[1]]$overallHealth)]][[1]] > 0)) {
  cat(fileList[[1]]$homophylyList[[length(fileList[[1]]$overallHealth)]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[length(fileList[[1]]$overallHealth)]][[3]] > 0)) {
  cat(fileList[[1]]$homophylyList[[length(fileList[[1]]$overallHealth)]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[length(fileList[[1]]$overallHealth)]][[2]] > 0)) {
  cat(fileList[[1]]$homophylyList[[length(fileList[[1]]$overallHealth)]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter {data-height=150} 

```{r}
diameter <- fileList[[1]]$totalNetworkInfo[[length(fileList[[1]]$overallHealth)]][[length(fileList[[1]]$overallHealth)]][[1]]
nodes <- length(fileList[[1]]$totalNetworkInfo[[length(fileList[[1]]$overallHealth)]][[10]])

# derive sector colours for gauge from nrow(nodes) and whether
# the graph is fragmented

if(graphConnected(fileList[[1]]$SSNQGraph[[length(fileList[[1]]$overallHealth)]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[1]]$SSNQGraph[[length(fileList[[1]]$overallHealth)]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships {data-height=150} 

```{r}
edgeDensity <- fileList[[1]]$totalNetworkInfo[[length(fileList[[1]]$overallHealth)]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity {data-height=150} 
  
```{r}
reciprocity <- fileList[[1]]$totalNetworkInfo[[length(fileList[[1]]$overallHealth)]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=550} 
<center>
```{r}

fileList[[1]]$dendrogramList[[length(fileList[[1]]$overallHealth)]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.


Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}

JSDataOverall1 <- jsonlite::read_json("D3JSDataOverall1.json")

repeatedforcedirectedOutput("repeatedforcedirectedOverall1")
output$repeatedforcedirectedOverall1 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSDataOverall1))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.


Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$HSList[[length(fileList[[1]]$overallHealth)]]) > 0) {
  cat(fileList[[1]]$HSList[[length(fileList[[1]]$overallHealth)]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[1]]$ASList[[length(fileList[[1]]$overallHealth)]]) > 0)) {
  cat(fileList[[1]]$ASList[[length(fileList[[1]]$overallHealth)]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[length(fileList[[1]]$overallHealth)]][[9]][1,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[length(fileList[[1]]$overallHealth)]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[length(fileList[[1]]$overallHealth)]][[9]][2,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[length(fileList[[1]]$overallHealth)]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[length(fileList[[1]]$overallHealth)]][[9]][3,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[length(fileList[[1]]$overallHealth)]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[1]]$isolatesList[[length(fileList[[1]]$overallHealth)]])) {
  cat(fileList[[1]]$isolatesList[[length(fileList[[1]]$overallHealth)]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.


Scots 7TGAN1 RQ1 Relationship Question {data-navmenu="Scots 7TGAN1"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### Question Statement: Relationships Question 1

```{r}
valueBox(
  "RQ1",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[1]]$className,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}




valueBox(
  fileList[[1]]$overallHealth[[1]][[1]],
  color = fileList[[1]]$overallHealth[[1]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[1]]$overallPfI[[1]][[1]],
  color = fileList[[1]]$overallPfI[[1]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[1]]$clientName`.

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[1]][[1]] > 0)) {
  cat(fileList[[1]]$homophylyList[[1]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[1]][[3]] > 0)) {
  cat(fileList[[1]]$homophylyList[[1]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[1]][[2]] > 0)) {
  cat(fileList[[1]]$homophylyList[[1]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter

```{r}

diameter <- fileList[[1]]$totalNetworkInfo[[1]][[4]][[1]]
nodes <- length(fileList[[1]]$totalNetworkInfo[[1]][[10]])

source("./assets/R/graphConnected.R")

if(graphConnected(fileList[[1]]$SSNQGraph[[1]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[1]]$SSNQGraph[[1]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships

```{r}
edgeDensity <- fileList[[1]]$totalNetworkInfo[[1]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity
  
```{r}
reciprocity <- fileList[[1]]$totalNetworkInfo[[1]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=400} 
<center>
```{r}

fileList[[1]]$dendrogramList[[1]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.
  

Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}
JSData11 <- jsonlite::read_json("D3JSData11.json")

repeatedforcedirectedOutput("repeatedforcedirected11")
output$repeatedforcedirected11 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSData11))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.

Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$HSList[[1]]) > 0) {
  cat(fileList[[1]]$HSList[[1]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[1]]$ASList[[1]]) > 0)) {
  cat(fileList[[1]]$ASList[[1]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[1]][[9]][1,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[1]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[1]][[9]][2,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[1]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[1]][[9]][3,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[1]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[1]]$isolatesList[[1]])) {
  cat(fileList[[1]]$isolatesList[[1]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.

Scots 7TGAN1 RQ2 Relationship Question {data-navmenu="Scots 7TGAN1"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### Question Statement: Relationships Question 2

```{r}
valueBox(
  "RQ2",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[1]]$className,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}




valueBox(
  fileList[[1]]$overallHealth[[2]][[1]],
  color = fileList[[1]]$overallHealth[[2]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[1]]$overallPfI[[2]][[1]],
  color = fileList[[1]]$overallPfI[[2]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[1]]$clientName`.

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[2]][[1]] > 0)) {
  cat(fileList[[1]]$homophylyList[[2]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[2]][[3]] > 0)) {
  cat(fileList[[1]]$homophylyList[[2]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[2]][[2]] > 0)) {
  cat(fileList[[1]]$homophylyList[[2]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter

```{r}

diameter <- fileList[[1]]$totalNetworkInfo[[2]][[4]][[1]]
nodes <- length(fileList[[1]]$totalNetworkInfo[[2]][[10]])

source("./assets/R/graphConnected.R")

if(graphConnected(fileList[[1]]$SSNQGraph[[2]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[1]]$SSNQGraph[[2]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships

```{r}
edgeDensity <- fileList[[1]]$totalNetworkInfo[[2]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity
  
```{r}
reciprocity <- fileList[[1]]$totalNetworkInfo[[2]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=400} 
<center>
```{r}

fileList[[1]]$dendrogramList[[2]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.
  

Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}
JSData12 <- jsonlite::read_json("D3JSData12.json")

repeatedforcedirectedOutput("repeatedforcedirected12")
output$repeatedforcedirected12 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSData12))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.

Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$HSList[[2]]) > 0) {
  cat(fileList[[1]]$HSList[[2]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[1]]$ASList[[2]]) > 0)) {
  cat(fileList[[1]]$ASList[[2]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[2]][[9]][1,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[2]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[2]][[9]][2,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[2]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[2]][[9]][3,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[2]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[1]]$isolatesList[[2]])) {
  cat(fileList[[1]]$isolatesList[[2]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.

Scots 7TGAN1 RQ3 Relationship Question {data-navmenu="Scots 7TGAN1"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### Question Statement: Relationships Question 3

```{r}
valueBox(
  "RQ3",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[1]]$className,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}




valueBox(
  fileList[[1]]$overallHealth[[3]][[1]],
  color = fileList[[1]]$overallHealth[[3]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[1]]$overallPfI[[3]][[1]],
  color = fileList[[1]]$overallPfI[[3]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[1]]$clientName`.

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[3]][[1]] > 0)) {
  cat(fileList[[1]]$homophylyList[[3]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[3]][[3]] > 0)) {
  cat(fileList[[1]]$homophylyList[[3]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$homophylyList[[3]][[2]] > 0)) {
  cat(fileList[[1]]$homophylyList[[3]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter

```{r}

diameter <- fileList[[1]]$totalNetworkInfo[[3]][[4]][[1]]
nodes <- length(fileList[[1]]$totalNetworkInfo[[3]][[10]])

source("./assets/R/graphConnected.R")

if(graphConnected(fileList[[1]]$SSNQGraph[[3]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[1]]$SSNQGraph[[3]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships

```{r}
edgeDensity <- fileList[[1]]$totalNetworkInfo[[3]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity
  
```{r}
reciprocity <- fileList[[1]]$totalNetworkInfo[[3]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=400} 
<center>
```{r}

fileList[[1]]$dendrogramList[[3]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.
  

Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}
JSData13 <- jsonlite::read_json("D3JSData13.json")

repeatedforcedirectedOutput("repeatedforcedirected13")
output$repeatedforcedirected13 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSData13))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.

Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[1]]$HSList[[3]]) > 0) {
  cat(fileList[[1]]$HSList[[3]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[1]]$ASList[[3]]) > 0)) {
  cat(fileList[[1]]$ASList[[3]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[3]][[9]][1,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[3]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[3]][[9]][2,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[3]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[1]]$totalNetworkInfo[[3]][[9]][3,1], "<br>", "and<br>",
          fileList[[1]]$totalNetworkInfo[[3]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[1]]$isolatesList[[3]])) {
  cat(fileList[[1]]$isolatesList[[3]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.

Student - Student Individual Profiles {data-navmenu="Scots 7TGAN1"}
=======================================================================

Individual Profiles {data-width=900 .tabset}
-----------------------------------------------------------------------



### RQ1

```{r}
renderPlotly ({
  fileList[[1]]$polarGraphList[[1]]
})
```

> Scores for each person for how well they report knowing one another can be explored here.  Click on the person's name in the list to visualise the scores and hover over the graph for more details.  Select multiple people to overlay their scores for comparison.  The green dotted line is the average score given by the network.



Degree {.tabset}
-----------------------------------------------------------------------



### RQ1

#### 'RQ1' Degree All Scores

```{r}
renderPlotly ({
  fileList[[1]]$degreeAllHistogramList[[1]]
})
```

> The higher the overall degree score, the more tied in the person is to the class.  Those learners who score nearest the average are those who are best placed to develop resiliency in the relational network of the class when they are encouraged to relate to one another, because they have connections to bring to bear, and have relational overhead to be able to develop further relationships without others suffering from divided attention.

#### 'RQ1' Degree In Scores

```{r}
renderPlotly ({
  fileList[[1]]$degreeInHistogramList[[1]]
})
```

> A higher 'Degree in' score indicates that more people in the class come
to this person for information

#### 'RQ1' Degree Out Scores

```{r}
renderPlotly({
  fileList[[1]]$degreeOutHistogramList[[1]]
})
```

> A higher 'Degree out' score indicates that the person is well connected within the class.

Scots 7TGAN2 Class Summary {data-navmenu="Scots 7TGAN2"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### These findings are an amalgamation of each peer-to-peer question asked of the learners.

```{r}
valueBox(
  "Overall",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[2]]$`Scots 7TGAN2`,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}
valueBox(
  fileList[[2]]$overallHealth[[length(fileList[[2]]$overallHealth)]][[1]],
  color = fileList[[2]]$overallHealth[[length(fileList[[2]]$overallHealth)]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[2]]$overallPfI[[length(fileList[[2]]$overallHealth)]][[1]],
  color = fileList[[2]]$overallPfI[[length(fileList[[2]]$overallHealth)]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[2]]$clientName`.

  Our analysis shows this class to be moderately healthy and with a moderate potential for improvement.
  

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[2]]$homophylyList[[length(fileList[[2]]$overallHealth)]][[1]] > 0)) {
  cat(fileList[[2]]$homophylyList[[length(fileList[[2]]$overallHealth)]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[2]]$homophylyList[[length(fileList[[2]]$overallHealth)]][[3]] > 0)) {
  cat(fileList[[2]]$homophylyList[[length(fileList[[2]]$overallHealth)]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[2]]$homophylyList[[length(fileList[[2]]$overallHealth)]][[2]] > 0)) {
  cat(fileList[[2]]$homophylyList[[length(fileList[[2]]$overallHealth)]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter {data-height=150} 

```{r}
diameter <- fileList[[2]]$totalNetworkInfo[[length(fileList[[2]]$overallHealth)]][[length(fileList[[2]]$overallHealth)]][[1]]
nodes <- length(fileList[[2]]$totalNetworkInfo[[length(fileList[[2]]$overallHealth)]][[10]])

# derive sector colours for gauge from nrow(nodes) and whether
# the graph is fragmented

if(graphConnected(fileList[[2]]$SSNQGraph[[length(fileList[[2]]$overallHealth)]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[2]]$SSNQGraph[[length(fileList[[2]]$overallHealth)]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships {data-height=150} 

```{r}
edgeDensity <- fileList[[2]]$totalNetworkInfo[[length(fileList[[2]]$overallHealth)]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity {data-height=150} 
  
```{r}
reciprocity <- fileList[[2]]$totalNetworkInfo[[length(fileList[[2]]$overallHealth)]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=550} 
<center>
```{r}

fileList[[2]]$dendrogramList[[length(fileList[[2]]$overallHealth)]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.


Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}

JSDataOverall2 <- jsonlite::read_json("D3JSDataOverall2.json")

repeatedforcedirectedOutput("repeatedforcedirectedOverall2")
output$repeatedforcedirectedOverall2 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSDataOverall2))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.


Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[2]]$HSList[[length(fileList[[2]]$overallHealth)]]) > 0) {
  cat(fileList[[2]]$HSList[[length(fileList[[2]]$overallHealth)]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[2]]$ASList[[length(fileList[[2]]$overallHealth)]]) > 0)) {
  cat(fileList[[2]]$ASList[[length(fileList[[2]]$overallHealth)]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[2]]$totalNetworkInfo[[length(fileList[[2]]$overallHealth)]][[9]][1,1], "<br>", "and<br>",
          fileList[[2]]$totalNetworkInfo[[length(fileList[[2]]$overallHealth)]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[2]]$totalNetworkInfo[[length(fileList[[2]]$overallHealth)]][[9]][2,1], "<br>", "and<br>",
          fileList[[2]]$totalNetworkInfo[[length(fileList[[2]]$overallHealth)]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[2]]$totalNetworkInfo[[length(fileList[[2]]$overallHealth)]][[9]][3,1], "<br>", "and<br>",
          fileList[[2]]$totalNetworkInfo[[length(fileList[[2]]$overallHealth)]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[2]]$isolatesList[[length(fileList[[2]]$overallHealth)]])) {
  cat(fileList[[2]]$isolatesList[[length(fileList[[2]]$overallHealth)]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.


Scots 7TGAN2 RQ1 Relationship Question {data-navmenu="Scots 7TGAN2"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### Question Statement: Relationships Question 1

```{r}
valueBox(
  "RQ1",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[2]]$className,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}




valueBox(
  fileList[[2]]$overallHealth[[1]][[1]],
  color = fileList[[2]]$overallHealth[[1]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[2]]$overallPfI[[1]][[1]],
  color = fileList[[2]]$overallPfI[[1]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[2]]$clientName`.

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[2]]$homophylyList[[1]][[1]] > 0)) {
  cat(fileList[[2]]$homophylyList[[1]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[2]]$homophylyList[[1]][[3]] > 0)) {
  cat(fileList[[2]]$homophylyList[[1]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[2]]$homophylyList[[1]][[2]] > 0)) {
  cat(fileList[[2]]$homophylyList[[1]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter

```{r}

diameter <- fileList[[2]]$totalNetworkInfo[[1]][[4]][[1]]
nodes <- length(fileList[[2]]$totalNetworkInfo[[1]][[10]])

source("./assets/R/graphConnected.R")

if(graphConnected(fileList[[2]]$SSNQGraph[[1]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[2]]$SSNQGraph[[1]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships

```{r}
edgeDensity <- fileList[[2]]$totalNetworkInfo[[1]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity
  
```{r}
reciprocity <- fileList[[2]]$totalNetworkInfo[[1]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=400} 
<center>
```{r}

fileList[[2]]$dendrogramList[[1]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.
  

Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}
JSData21 <- jsonlite::read_json("D3JSData21.json")

repeatedforcedirectedOutput("repeatedforcedirected21")
output$repeatedforcedirected21 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSData21))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.

Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[2]]$HSList[[1]]) > 0) {
  cat(fileList[[2]]$HSList[[1]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[2]]$ASList[[1]]) > 0)) {
  cat(fileList[[2]]$ASList[[1]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[2]]$totalNetworkInfo[[1]][[9]][1,1], "<br>", "and<br>",
          fileList[[2]]$totalNetworkInfo[[1]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[2]]$totalNetworkInfo[[1]][[9]][2,1], "<br>", "and<br>",
          fileList[[2]]$totalNetworkInfo[[1]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[2]]$totalNetworkInfo[[1]][[9]][3,1], "<br>", "and<br>",
          fileList[[2]]$totalNetworkInfo[[1]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[2]]$isolatesList[[1]])) {
  cat(fileList[[2]]$isolatesList[[1]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.

Scots 7TGAN2 RQ2 Relationship Question {data-navmenu="Scots 7TGAN2"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### Question Statement: Relationships Question 2

```{r}
valueBox(
  "RQ2",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[2]]$className,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}




valueBox(
  fileList[[2]]$overallHealth[[2]][[1]],
  color = fileList[[2]]$overallHealth[[2]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[2]]$overallPfI[[2]][[1]],
  color = fileList[[2]]$overallPfI[[2]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[2]]$clientName`.

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[2]]$homophylyList[[2]][[1]] > 0)) {
  cat(fileList[[2]]$homophylyList[[2]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[2]]$homophylyList[[2]][[3]] > 0)) {
  cat(fileList[[2]]$homophylyList[[2]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[2]]$homophylyList[[2]][[2]] > 0)) {
  cat(fileList[[2]]$homophylyList[[2]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter

```{r}

diameter <- fileList[[2]]$totalNetworkInfo[[2]][[4]][[1]]
nodes <- length(fileList[[2]]$totalNetworkInfo[[2]][[10]])

source("./assets/R/graphConnected.R")

if(graphConnected(fileList[[2]]$SSNQGraph[[2]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[2]]$SSNQGraph[[2]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships

```{r}
edgeDensity <- fileList[[2]]$totalNetworkInfo[[2]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity
  
```{r}
reciprocity <- fileList[[2]]$totalNetworkInfo[[2]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=400} 
<center>
```{r}

fileList[[2]]$dendrogramList[[2]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.
  

Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}
JSData22 <- jsonlite::read_json("D3JSData22.json")

repeatedforcedirectedOutput("repeatedforcedirected22")
output$repeatedforcedirected22 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSData22))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.

Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[2]]$HSList[[2]]) > 0) {
  cat(fileList[[2]]$HSList[[2]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[2]]$ASList[[2]]) > 0)) {
  cat(fileList[[2]]$ASList[[2]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[2]]$totalNetworkInfo[[2]][[9]][1,1], "<br>", "and<br>",
          fileList[[2]]$totalNetworkInfo[[2]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[2]]$totalNetworkInfo[[2]][[9]][2,1], "<br>", "and<br>",
          fileList[[2]]$totalNetworkInfo[[2]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[2]]$totalNetworkInfo[[2]][[9]][3,1], "<br>", "and<br>",
          fileList[[2]]$totalNetworkInfo[[2]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[2]]$isolatesList[[2]])) {
  cat(fileList[[2]]$isolatesList[[2]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.

Scots 7TGAN2 RQ3 Relationship Question {data-navmenu="Scots 7TGAN2"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### Question Statement: Relationships Question 3

```{r}
valueBox(
  "RQ3",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[2]]$className,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}




valueBox(
  fileList[[2]]$overallHealth[[3]][[1]],
  color = fileList[[2]]$overallHealth[[3]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[2]]$overallPfI[[3]][[1]],
  color = fileList[[2]]$overallPfI[[3]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[2]]$clientName`.

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[2]]$homophylyList[[3]][[1]] > 0)) {
  cat(fileList[[2]]$homophylyList[[3]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[2]]$homophylyList[[3]][[3]] > 0)) {
  cat(fileList[[2]]$homophylyList[[3]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[2]]$homophylyList[[3]][[2]] > 0)) {
  cat(fileList[[2]]$homophylyList[[3]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter

```{r}

diameter <- fileList[[2]]$totalNetworkInfo[[3]][[4]][[1]]
nodes <- length(fileList[[2]]$totalNetworkInfo[[3]][[10]])

source("./assets/R/graphConnected.R")

if(graphConnected(fileList[[2]]$SSNQGraph[[3]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[2]]$SSNQGraph[[3]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships

```{r}
edgeDensity <- fileList[[2]]$totalNetworkInfo[[3]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity
  
```{r}
reciprocity <- fileList[[2]]$totalNetworkInfo[[3]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=400} 
<center>
```{r}

fileList[[2]]$dendrogramList[[3]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.
  

Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}
JSData23 <- jsonlite::read_json("D3JSData23.json")

repeatedforcedirectedOutput("repeatedforcedirected23")
output$repeatedforcedirected23 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSData23))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.

Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[2]]$HSList[[3]]) > 0) {
  cat(fileList[[2]]$HSList[[3]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[2]]$ASList[[3]]) > 0)) {
  cat(fileList[[2]]$ASList[[3]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[2]]$totalNetworkInfo[[3]][[9]][1,1], "<br>", "and<br>",
          fileList[[2]]$totalNetworkInfo[[3]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[2]]$totalNetworkInfo[[3]][[9]][2,1], "<br>", "and<br>",
          fileList[[2]]$totalNetworkInfo[[3]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[2]]$totalNetworkInfo[[3]][[9]][3,1], "<br>", "and<br>",
          fileList[[2]]$totalNetworkInfo[[3]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[2]]$isolatesList[[3]])) {
  cat(fileList[[2]]$isolatesList[[3]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.

Student - Student Individual Profiles {data-navmenu="Scots 7TGAN2"}
=======================================================================

Individual Profiles {data-width=900 .tabset}
-----------------------------------------------------------------------



### RQ1

```{r}
renderPlotly ({
  fileList[[2]]$polarGraphList[[1]]
})
```

> Scores for each person for how well they report knowing one another can be explored here.  Click on the person's name in the list to visualise the scores and hover over the graph for more details.  Select multiple people to overlay their scores for comparison.  The green dotted line is the average score given by the network.



Degree {.tabset}
-----------------------------------------------------------------------



### RQ1

#### 'RQ1' Degree All Scores

```{r}
renderPlotly ({
  fileList[[2]]$degreeAllHistogramList[[1]]
})
```

> The higher the overall degree score, the more tied in the person is to the class.  Those learners who score nearest the average are those who are best placed to develop resiliency in the relational network of the class when they are encouraged to relate to one another, because they have connections to bring to bear, and have relational overhead to be able to develop further relationships without others suffering from divided attention.

#### 'RQ1' Degree In Scores

```{r}
renderPlotly ({
  fileList[[2]]$degreeInHistogramList[[1]]
})
```

> A higher 'Degree in' score indicates that more people in the class come
to this person for information

#### 'RQ1' Degree Out Scores

```{r}
renderPlotly({
  fileList[[2]]$degreeOutHistogramList[[1]]
})
```

> A higher 'Degree out' score indicates that the person is well connected within the class.

Scots 7TGAR1 Class Summary {data-navmenu="Scots 7TGAR1"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### These findings are an amalgamation of each peer-to-peer question asked of the learners.

```{r}
valueBox(
  "Overall",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[3]]$`Scots 7TGAR1`,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}
valueBox(
  fileList[[3]]$overallHealth[[length(fileList[[3]]$overallHealth)]][[1]],
  color = fileList[[3]]$overallHealth[[length(fileList[[3]]$overallHealth)]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[3]]$overallPfI[[length(fileList[[3]]$overallHealth)]][[1]],
  color = fileList[[3]]$overallPfI[[length(fileList[[3]]$overallHealth)]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[3]]$clientName`.

  Our analysis shows this class to be moderately healthy and with a moderate potential for improvement.
  

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[3]]$homophylyList[[length(fileList[[3]]$overallHealth)]][[1]] > 0)) {
  cat(fileList[[3]]$homophylyList[[length(fileList[[3]]$overallHealth)]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[3]]$homophylyList[[length(fileList[[3]]$overallHealth)]][[3]] > 0)) {
  cat(fileList[[3]]$homophylyList[[length(fileList[[3]]$overallHealth)]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[3]]$homophylyList[[length(fileList[[3]]$overallHealth)]][[2]] > 0)) {
  cat(fileList[[3]]$homophylyList[[length(fileList[[3]]$overallHealth)]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter {data-height=150} 

```{r}
diameter <- fileList[[3]]$totalNetworkInfo[[length(fileList[[3]]$overallHealth)]][[length(fileList[[3]]$overallHealth)]][[1]]
nodes <- length(fileList[[3]]$totalNetworkInfo[[length(fileList[[3]]$overallHealth)]][[10]])

# derive sector colours for gauge from nrow(nodes) and whether
# the graph is fragmented

if(graphConnected(fileList[[3]]$SSNQGraph[[length(fileList[[3]]$overallHealth)]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[3]]$SSNQGraph[[length(fileList[[3]]$overallHealth)]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships {data-height=150} 

```{r}
edgeDensity <- fileList[[3]]$totalNetworkInfo[[length(fileList[[3]]$overallHealth)]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity {data-height=150} 
  
```{r}
reciprocity <- fileList[[3]]$totalNetworkInfo[[length(fileList[[3]]$overallHealth)]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=550} 
<center>
```{r}

fileList[[3]]$dendrogramList[[length(fileList[[3]]$overallHealth)]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.


Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}

JSDataOverall3 <- jsonlite::read_json("D3JSDataOverall3.json")

repeatedforcedirectedOutput("repeatedforcedirectedOverall3")
output$repeatedforcedirectedOverall3 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSDataOverall3))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.


Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[3]]$HSList[[length(fileList[[3]]$overallHealth)]]) > 0) {
  cat(fileList[[3]]$HSList[[length(fileList[[3]]$overallHealth)]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[3]]$ASList[[length(fileList[[3]]$overallHealth)]]) > 0)) {
  cat(fileList[[3]]$ASList[[length(fileList[[3]]$overallHealth)]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[3]]$totalNetworkInfo[[length(fileList[[3]]$overallHealth)]][[9]][1,1], "<br>", "and<br>",
          fileList[[3]]$totalNetworkInfo[[length(fileList[[3]]$overallHealth)]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[3]]$totalNetworkInfo[[length(fileList[[3]]$overallHealth)]][[9]][2,1], "<br>", "and<br>",
          fileList[[3]]$totalNetworkInfo[[length(fileList[[3]]$overallHealth)]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[3]]$totalNetworkInfo[[length(fileList[[3]]$overallHealth)]][[9]][3,1], "<br>", "and<br>",
          fileList[[3]]$totalNetworkInfo[[length(fileList[[3]]$overallHealth)]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[3]]$isolatesList[[length(fileList[[3]]$overallHealth)]])) {
  cat(fileList[[3]]$isolatesList[[length(fileList[[3]]$overallHealth)]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.


Scots 7TGAR1 RQ1 Relationship Question {data-navmenu="Scots 7TGAR1"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### Question Statement: Relationships Question 1

```{r}
valueBox(
  "RQ1",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[3]]$className,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}




valueBox(
  fileList[[3]]$overallHealth[[1]][[1]],
  color = fileList[[3]]$overallHealth[[1]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[3]]$overallPfI[[1]][[1]],
  color = fileList[[3]]$overallPfI[[1]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[3]]$clientName`.

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[3]]$homophylyList[[1]][[1]] > 0)) {
  cat(fileList[[3]]$homophylyList[[1]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[3]]$homophylyList[[1]][[3]] > 0)) {
  cat(fileList[[3]]$homophylyList[[1]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[3]]$homophylyList[[1]][[2]] > 0)) {
  cat(fileList[[3]]$homophylyList[[1]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter

```{r}

diameter <- fileList[[3]]$totalNetworkInfo[[1]][[4]][[1]]
nodes <- length(fileList[[3]]$totalNetworkInfo[[1]][[10]])

source("./assets/R/graphConnected.R")

if(graphConnected(fileList[[3]]$SSNQGraph[[1]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[3]]$SSNQGraph[[1]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships

```{r}
edgeDensity <- fileList[[3]]$totalNetworkInfo[[1]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity
  
```{r}
reciprocity <- fileList[[3]]$totalNetworkInfo[[1]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=400} 
<center>
```{r}

fileList[[3]]$dendrogramList[[1]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.
  

Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}
JSData31 <- jsonlite::read_json("D3JSData31.json")

repeatedforcedirectedOutput("repeatedforcedirected31")
output$repeatedforcedirected31 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSData31))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.

Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[3]]$HSList[[1]]) > 0) {
  cat(fileList[[3]]$HSList[[1]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[3]]$ASList[[1]]) > 0)) {
  cat(fileList[[3]]$ASList[[1]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[3]]$totalNetworkInfo[[1]][[9]][1,1], "<br>", "and<br>",
          fileList[[3]]$totalNetworkInfo[[1]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[3]]$totalNetworkInfo[[1]][[9]][2,1], "<br>", "and<br>",
          fileList[[3]]$totalNetworkInfo[[1]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[3]]$totalNetworkInfo[[1]][[9]][3,1], "<br>", "and<br>",
          fileList[[3]]$totalNetworkInfo[[1]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[3]]$isolatesList[[1]])) {
  cat(fileList[[3]]$isolatesList[[1]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.

Scots 7TGAR1 RQ2 Relationship Question {data-navmenu="Scots 7TGAR1"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### Question Statement: Relationships Question 2

```{r}
valueBox(
  "RQ2",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[3]]$className,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}




valueBox(
  fileList[[3]]$overallHealth[[2]][[1]],
  color = fileList[[3]]$overallHealth[[2]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[3]]$overallPfI[[2]][[1]],
  color = fileList[[3]]$overallPfI[[2]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[3]]$clientName`.

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[3]]$homophylyList[[2]][[1]] > 0)) {
  cat(fileList[[3]]$homophylyList[[2]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[3]]$homophylyList[[2]][[3]] > 0)) {
  cat(fileList[[3]]$homophylyList[[2]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[3]]$homophylyList[[2]][[2]] > 0)) {
  cat(fileList[[3]]$homophylyList[[2]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter

```{r}

diameter <- fileList[[3]]$totalNetworkInfo[[2]][[4]][[1]]
nodes <- length(fileList[[3]]$totalNetworkInfo[[2]][[10]])

source("./assets/R/graphConnected.R")

if(graphConnected(fileList[[3]]$SSNQGraph[[2]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[3]]$SSNQGraph[[2]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships

```{r}
edgeDensity <- fileList[[3]]$totalNetworkInfo[[2]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity
  
```{r}
reciprocity <- fileList[[3]]$totalNetworkInfo[[2]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=400} 
<center>
```{r}

fileList[[3]]$dendrogramList[[2]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.
  

Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}
JSData32 <- jsonlite::read_json("D3JSData32.json")

repeatedforcedirectedOutput("repeatedforcedirected32")
output$repeatedforcedirected32 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSData32))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.

Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[3]]$HSList[[2]]) > 0) {
  cat(fileList[[3]]$HSList[[2]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[3]]$ASList[[2]]) > 0)) {
  cat(fileList[[3]]$ASList[[2]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[3]]$totalNetworkInfo[[2]][[9]][1,1], "<br>", "and<br>",
          fileList[[3]]$totalNetworkInfo[[2]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[3]]$totalNetworkInfo[[2]][[9]][2,1], "<br>", "and<br>",
          fileList[[3]]$totalNetworkInfo[[2]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[3]]$totalNetworkInfo[[2]][[9]][3,1], "<br>", "and<br>",
          fileList[[3]]$totalNetworkInfo[[2]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[3]]$isolatesList[[2]])) {
  cat(fileList[[3]]$isolatesList[[2]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.

Scots 7TGAR1 RQ3 Relationship Question {data-navmenu="Scots 7TGAR1"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### Question Statement: Relationships Question 3

```{r}
valueBox(
  "RQ3",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[3]]$className,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}




valueBox(
  fileList[[3]]$overallHealth[[3]][[1]],
  color = fileList[[3]]$overallHealth[[3]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[3]]$overallPfI[[3]][[1]],
  color = fileList[[3]]$overallPfI[[3]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[3]]$clientName`.

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[3]]$homophylyList[[3]][[1]] > 0)) {
  cat(fileList[[3]]$homophylyList[[3]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[3]]$homophylyList[[3]][[3]] > 0)) {
  cat(fileList[[3]]$homophylyList[[3]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[3]]$homophylyList[[3]][[2]] > 0)) {
  cat(fileList[[3]]$homophylyList[[3]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter

```{r}

diameter <- fileList[[3]]$totalNetworkInfo[[3]][[4]][[1]]
nodes <- length(fileList[[3]]$totalNetworkInfo[[3]][[10]])

source("./assets/R/graphConnected.R")

if(graphConnected(fileList[[3]]$SSNQGraph[[3]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[3]]$SSNQGraph[[3]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships

```{r}
edgeDensity <- fileList[[3]]$totalNetworkInfo[[3]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity
  
```{r}
reciprocity <- fileList[[3]]$totalNetworkInfo[[3]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=400} 
<center>
```{r}

fileList[[3]]$dendrogramList[[3]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.
  

Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}
JSData33 <- jsonlite::read_json("D3JSData33.json")

repeatedforcedirectedOutput("repeatedforcedirected33")
output$repeatedforcedirected33 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSData33))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.

Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[3]]$HSList[[3]]) > 0) {
  cat(fileList[[3]]$HSList[[3]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[3]]$ASList[[3]]) > 0)) {
  cat(fileList[[3]]$ASList[[3]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[3]]$totalNetworkInfo[[3]][[9]][1,1], "<br>", "and<br>",
          fileList[[3]]$totalNetworkInfo[[3]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[3]]$totalNetworkInfo[[3]][[9]][2,1], "<br>", "and<br>",
          fileList[[3]]$totalNetworkInfo[[3]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[3]]$totalNetworkInfo[[3]][[9]][3,1], "<br>", "and<br>",
          fileList[[3]]$totalNetworkInfo[[3]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[3]]$isolatesList[[3]])) {
  cat(fileList[[3]]$isolatesList[[3]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.

Student - Student Individual Profiles {data-navmenu="Scots 7TGAR1"}
=======================================================================

Individual Profiles {data-width=900 .tabset}
-----------------------------------------------------------------------



### RQ1

```{r}
renderPlotly ({
  fileList[[3]]$polarGraphList[[1]]
})
```

> Scores for each person for how well they report knowing one another can be explored here.  Click on the person's name in the list to visualise the scores and hover over the graph for more details.  Select multiple people to overlay their scores for comparison.  The green dotted line is the average score given by the network.



Degree {.tabset}
-----------------------------------------------------------------------



### RQ1

#### 'RQ1' Degree All Scores

```{r}
renderPlotly ({
  fileList[[3]]$degreeAllHistogramList[[1]]
})
```

> The higher the overall degree score, the more tied in the person is to the class.  Those learners who score nearest the average are those who are best placed to develop resiliency in the relational network of the class when they are encouraged to relate to one another, because they have connections to bring to bear, and have relational overhead to be able to develop further relationships without others suffering from divided attention.

#### 'RQ1' Degree In Scores

```{r}
renderPlotly ({
  fileList[[3]]$degreeInHistogramList[[1]]
})
```

> A higher 'Degree in' score indicates that more people in the class come
to this person for information

#### 'RQ1' Degree Out Scores

```{r}
renderPlotly({
  fileList[[3]]$degreeOutHistogramList[[1]]
})
```

> A higher 'Degree out' score indicates that the person is well connected within the class.

Scots 7TGAR2 Class Summary {data-navmenu="Scots 7TGAR2"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### These findings are an amalgamation of each peer-to-peer question asked of the learners.

```{r}
valueBox(
  "Overall",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[4]]$`Scots 7TGAR2`,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}
valueBox(
  fileList[[4]]$overallHealth[[length(fileList[[4]]$overallHealth)]][[1]],
  color = fileList[[4]]$overallHealth[[length(fileList[[4]]$overallHealth)]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[4]]$overallPfI[[length(fileList[[4]]$overallHealth)]][[1]],
  color = fileList[[4]]$overallPfI[[length(fileList[[4]]$overallHealth)]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[4]]$clientName`.

  Our analysis shows this class to be moderately healthy and with a moderate potential for improvement.
  

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[4]]$homophylyList[[length(fileList[[4]]$overallHealth)]][[1]] > 0)) {
  cat(fileList[[4]]$homophylyList[[length(fileList[[4]]$overallHealth)]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[4]]$homophylyList[[length(fileList[[4]]$overallHealth)]][[3]] > 0)) {
  cat(fileList[[4]]$homophylyList[[length(fileList[[4]]$overallHealth)]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[4]]$homophylyList[[length(fileList[[4]]$overallHealth)]][[2]] > 0)) {
  cat(fileList[[4]]$homophylyList[[length(fileList[[4]]$overallHealth)]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter {data-height=150} 

```{r}
diameter <- fileList[[4]]$totalNetworkInfo[[length(fileList[[4]]$overallHealth)]][[length(fileList[[4]]$overallHealth)]][[1]]
nodes <- length(fileList[[4]]$totalNetworkInfo[[length(fileList[[4]]$overallHealth)]][[10]])

# derive sector colours for gauge from nrow(nodes) and whether
# the graph is fragmented

if(graphConnected(fileList[[4]]$SSNQGraph[[length(fileList[[4]]$overallHealth)]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[4]]$SSNQGraph[[length(fileList[[4]]$overallHealth)]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships {data-height=150} 

```{r}
edgeDensity <- fileList[[4]]$totalNetworkInfo[[length(fileList[[4]]$overallHealth)]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity {data-height=150} 
  
```{r}
reciprocity <- fileList[[4]]$totalNetworkInfo[[length(fileList[[4]]$overallHealth)]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=550} 
<center>
```{r}

fileList[[4]]$dendrogramList[[length(fileList[[4]]$overallHealth)]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.


Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}

JSDataOverall4 <- jsonlite::read_json("D3JSDataOverall4.json")

repeatedforcedirectedOutput("repeatedforcedirectedOverall4")
output$repeatedforcedirectedOverall4 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSDataOverall4))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.


Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[4]]$HSList[[length(fileList[[4]]$overallHealth)]]) > 0) {
  cat(fileList[[4]]$HSList[[length(fileList[[4]]$overallHealth)]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[4]]$ASList[[length(fileList[[4]]$overallHealth)]]) > 0)) {
  cat(fileList[[4]]$ASList[[length(fileList[[4]]$overallHealth)]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[4]]$totalNetworkInfo[[length(fileList[[4]]$overallHealth)]][[9]][1,1], "<br>", "and<br>",
          fileList[[4]]$totalNetworkInfo[[length(fileList[[4]]$overallHealth)]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[4]]$totalNetworkInfo[[length(fileList[[4]]$overallHealth)]][[9]][2,1], "<br>", "and<br>",
          fileList[[4]]$totalNetworkInfo[[length(fileList[[4]]$overallHealth)]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[4]]$totalNetworkInfo[[length(fileList[[4]]$overallHealth)]][[9]][3,1], "<br>", "and<br>",
          fileList[[4]]$totalNetworkInfo[[length(fileList[[4]]$overallHealth)]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[4]]$isolatesList[[length(fileList[[4]]$overallHealth)]])) {
  cat(fileList[[4]]$isolatesList[[length(fileList[[4]]$overallHealth)]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.


Scots 7TGAR2 RQ1 Relationship Question {data-navmenu="Scots 7TGAR2"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### Question Statement: Relationships Question 1

```{r}
valueBox(
  "RQ1",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[4]]$className,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}




valueBox(
  fileList[[4]]$overallHealth[[1]][[1]],
  color = fileList[[4]]$overallHealth[[1]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[4]]$overallPfI[[1]][[1]],
  color = fileList[[4]]$overallPfI[[1]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[4]]$clientName`.

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[4]]$homophylyList[[1]][[1]] > 0)) {
  cat(fileList[[4]]$homophylyList[[1]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[4]]$homophylyList[[1]][[3]] > 0)) {
  cat(fileList[[4]]$homophylyList[[1]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[4]]$homophylyList[[1]][[2]] > 0)) {
  cat(fileList[[4]]$homophylyList[[1]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter

```{r}

diameter <- fileList[[4]]$totalNetworkInfo[[1]][[4]][[1]]
nodes <- length(fileList[[4]]$totalNetworkInfo[[1]][[10]])

source("./assets/R/graphConnected.R")

if(graphConnected(fileList[[4]]$SSNQGraph[[1]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[4]]$SSNQGraph[[1]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships

```{r}
edgeDensity <- fileList[[4]]$totalNetworkInfo[[1]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity
  
```{r}
reciprocity <- fileList[[4]]$totalNetworkInfo[[1]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=400} 
<center>
```{r}

fileList[[4]]$dendrogramList[[1]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.
  

Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}
JSData41 <- jsonlite::read_json("D3JSData41.json")

repeatedforcedirectedOutput("repeatedforcedirected41")
output$repeatedforcedirected41 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSData41))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.

Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[4]]$HSList[[1]]) > 0) {
  cat(fileList[[4]]$HSList[[1]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[4]]$ASList[[1]]) > 0)) {
  cat(fileList[[4]]$ASList[[1]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[4]]$totalNetworkInfo[[1]][[9]][1,1], "<br>", "and<br>",
          fileList[[4]]$totalNetworkInfo[[1]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[4]]$totalNetworkInfo[[1]][[9]][2,1], "<br>", "and<br>",
          fileList[[4]]$totalNetworkInfo[[1]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[4]]$totalNetworkInfo[[1]][[9]][3,1], "<br>", "and<br>",
          fileList[[4]]$totalNetworkInfo[[1]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[4]]$isolatesList[[1]])) {
  cat(fileList[[4]]$isolatesList[[1]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.

Scots 7TGAR2 RQ2 Relationship Question {data-navmenu="Scots 7TGAR2"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### Question Statement: Relationships Question 2

```{r}
valueBox(
  "RQ2",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[4]]$className,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}




valueBox(
  fileList[[4]]$overallHealth[[2]][[1]],
  color = fileList[[4]]$overallHealth[[2]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[4]]$overallPfI[[2]][[1]],
  color = fileList[[4]]$overallPfI[[2]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[4]]$clientName`.

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[4]]$homophylyList[[2]][[1]] > 0)) {
  cat(fileList[[4]]$homophylyList[[2]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[4]]$homophylyList[[2]][[3]] > 0)) {
  cat(fileList[[4]]$homophylyList[[2]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[4]]$homophylyList[[2]][[2]] > 0)) {
  cat(fileList[[4]]$homophylyList[[2]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter

```{r}

diameter <- fileList[[4]]$totalNetworkInfo[[2]][[4]][[1]]
nodes <- length(fileList[[4]]$totalNetworkInfo[[2]][[10]])

source("./assets/R/graphConnected.R")

if(graphConnected(fileList[[4]]$SSNQGraph[[2]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[4]]$SSNQGraph[[2]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships

```{r}
edgeDensity <- fileList[[4]]$totalNetworkInfo[[2]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity
  
```{r}
reciprocity <- fileList[[4]]$totalNetworkInfo[[2]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=400} 
<center>
```{r}

fileList[[4]]$dendrogramList[[2]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.
  

Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}
JSData42 <- jsonlite::read_json("D3JSData42.json")

repeatedforcedirectedOutput("repeatedforcedirected42")
output$repeatedforcedirected42 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSData42))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.

Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[4]]$HSList[[2]]) > 0) {
  cat(fileList[[4]]$HSList[[2]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[4]]$ASList[[2]]) > 0)) {
  cat(fileList[[4]]$ASList[[2]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[4]]$totalNetworkInfo[[2]][[9]][1,1], "<br>", "and<br>",
          fileList[[4]]$totalNetworkInfo[[2]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[4]]$totalNetworkInfo[[2]][[9]][2,1], "<br>", "and<br>",
          fileList[[4]]$totalNetworkInfo[[2]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[4]]$totalNetworkInfo[[2]][[9]][3,1], "<br>", "and<br>",
          fileList[[4]]$totalNetworkInfo[[2]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[4]]$isolatesList[[2]])) {
  cat(fileList[[4]]$isolatesList[[2]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.

Scots 7TGAR2 RQ3 Relationship Question {data-navmenu="Scots 7TGAR2"}
=======================================================================
  
Headlines {data-width=200}
--------------------------------------------------------------------------

### Question Statement: Relationships Question 3

```{r}
valueBox(
  "RQ3",
  caption = NULL,
  color = '#186ecc',
  icon = "fa-comment"
)
```

### {-}

```{r}
valueBox(
  fileList[[4]]$className,
  caption = NULL,
  color = '#186ecc',
  icon = "fa-chalkboard-teacher"
)
```

### Network Health

```{r}




valueBox(
  fileList[[4]]$overallHealth[[3]][[1]],
  color = fileList[[4]]$overallHealth[[3]][[2]],
  icon = "fa-file-medical"
)
```

### Potential for Improvement

```{r}
valueBox(
  fileList[[4]]$overallPfI[[3]][[1]],
  color = fileList[[4]]$overallPfI[[3]][[2]],
  icon = "fa-chart-line"
)
```

### Our Commentary

  The data shown here is a result of analysis conducted upon the social
network data provided by completing our Relationships Foundation
Questionnaires, along with any other information provided to us by you
and/or `r fileList[[4]]$clientName`.

### Class Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[4]]$homophylyList[[3]][[1]] > 0)) {
  cat(fileList[[4]]$homophylyList[[3]][[1]])
} else {
  cat("None")
}
```
</center>

>These factors statistically significantly influence the nature and function of the class

### Class Indeterminate Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[4]]$homophylyList[[3]][[3]] > 0)) {
  cat(fileList[[4]]$homophylyList[[3]][[3]])
} else {
  cat("None")
}
```
</center>

>These factors could not be shown to influence the nature and function of the class at a peer-to-peer level due to limitations in the data collected

### Class Non-Predictive Factors

<center>
```{r, results = 'asis'}
if (length(fileList[[4]]$homophylyList[[3]][[2]] > 0)) {
  cat(fileList[[4]]$homophylyList[[3]][[2]])
} else {
  cat("None")
}
```
</center>

>These factors do not statistically significantly influence the nature and
function of the class

Row {data-width=250}
-----------------------------------------------------------------------

### Class Diameter

```{r}

diameter <- fileList[[4]]$totalNetworkInfo[[3]][[4]][[1]]
nodes <- length(fileList[[4]]$totalNetworkInfo[[3]][[10]])

source("./assets/R/graphConnected.R")

if(graphConnected(fileList[[4]]$SSNQGraph[[3]])== F) {
  customSectors <-  gaugeSectors (
    danger = c(0, 100)
  )
} else {
  customSectors <-  gaugeSectors (
    success = c(0,(nodes/6)),
    warning = c((nodes/6), (nodes/3)),
    danger = c((nodes/3), (nodes/2)))
}

#make gauge
gauge(round(diameter, digits = 2), min = 1, max = (nodes/2), sectors = customSectors)

#provide warning text if graph is fragmented.
if (graphConnected(fileList[[4]]$SSNQGraph[[3]]) == F) {
  SSNQConnectedWarning <- paste("However, as this group is split across ",
    "separate unconnected sub-groups, this may not be a good measure of group ",
    "cohesiveness.",
    sep = "")
} else {
  SSNQConnectedWarning <- ""
}
```
 
> The most distant people are `r round(diameter, digits=0)` relationships away
from each other. <span style="color: red;">`r SSNQConnectedWarning`</span> 

### Percentage of Positive Relationships

```{r}
edgeDensity <- fileList[[4]]$totalNetworkInfo[[3]][[5]]
edgeDensityPercentage <- round((edgeDensity*100), digits = 0)
gauge(edgeDensityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(21, 100), 
    warning = c(16, 20), 
    danger = c(0, 15)
  ))
```
  
> `r round(edgeDensity, digits = 2)*100`% of all possible relationships are
strongly positive.
  
### Class Reciprocity
  
```{r}
reciprocity <- fileList[[4]]$totalNetworkInfo[[3]][[6]]
reciprocityPercentage <- round((reciprocity*100), digits = 0)
gauge(reciprocityPercentage, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(55, 100), 
    warning = c(40, 54), 
    danger = c(0, 39)
  ))
```

> Both parties agreed on a relationship status
`r round(reciprocity, digits = 2)*100`% of the time.

### Class Communities Dendrogram  {data-height=400} 
<center>
```{r}

fileList[[4]]$dendrogramList[[3]]

```
</center>

> This shows how the relational landscape divides into subgroups, mirrored in the colour of the dots on the summary graph.  The higher the number on the left, the bigger the distance between the group members attached at the split.
  

Network Maps 
----------------------------------------------------------------

### Summary graph {.no-padding data-height=700} 

```{r}
JSData43 <- jsonlite::read_json("D3JSData43.json")

repeatedforcedirectedOutput("repeatedforcedirected43")
output$repeatedforcedirected43 <- renderRepeatedforcedirected(repeatedforcedirected("Hello", JSData43))
```

> The lines on this graph represent the strongest relationships in the class. Each dot is a person, and each line is a strong relationship. The colours indicate cliques, or subgroups in the data which naturally form as people form and maintain social networks. Zoom using the scroll wheel or pinch on a touchscreen device, and drag people around to see who is connected most closely to them. The position on the graph doesn't matter itself, its about the position relative to the other people and how linked in they are with the group as a whole.

Key Network Information {data-width=250}
-----------------------------------------------------

### Class 'Hubs' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(fileList[[4]]$HSList[[3]]) > 0) {
  cat(fileList[[4]]$HSList[[3]])
} else {
  cat("Contact Volume Hub Analysis Encountered an Error")
}
```
</center>

> These people are the lifeblood of the class: Their absence would hamper communication and they make good contacts for new members to get more integrated.  They are those who report the most highly positive relationships with others.

### Class 'Authorities' {data-height=350} 

<center>
```{r, results = 'asis'}
if (length(as.character(fileList[[4]]$ASList[[3]]) > 0)) {
  cat(fileList[[4]]$ASList[[3]])
} else {
  cat("Network Authority Analysis Encountered an Error")
}
```
</center>

>These tend to be the class members who are  looked up to, or approached for advice or information by their peers: They have high value to others in the group.  They are those whom others identify as having the most highly positive relationships with.

### Fundamental Relationships  {data-height=750}

<center>
```{r, results = 'asis'}
cat(paste(fileList[[4]]$totalNetworkInfo[[3]][[9]][1,1], "<br>", "and<br>",
          fileList[[4]]$totalNetworkInfo[[3]][[9]][1,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[4]]$totalNetworkInfo[[3]][[9]][2,1], "<br>", "and<br>",
          fileList[[4]]$totalNetworkInfo[[3]][[9]][2,2])
    )
```

***

```{r, results = 'asis'}
cat(paste(fileList[[4]]$totalNetworkInfo[[3]][[9]][3,1], "<br>", "and<br>",
          fileList[[4]]$totalNetworkInfo[[3]][[9]][3,2])
    )
```
</center>

>These are the relationships which make the class operate as it does.  Promoting
these adds cohesion.

### Network Isolates

<center>
```{r, results = 'asis'}
if(!is.null(fileList[[4]]$isolatesList[[3]])) {
  cat(fileList[[4]]$isolatesList[[3]])
}
```
</center>

>These people are not joined to any others in the network by positive
relationships in at least one of the dimensions they were asked about.

Student - Student Individual Profiles {data-navmenu="Scots 7TGAR2"}
=======================================================================

Individual Profiles {data-width=900 .tabset}
-----------------------------------------------------------------------



### RQ1

```{r}
renderPlotly ({
  fileList[[4]]$polarGraphList[[1]]
})
```

> Scores for each person for how well they report knowing one another can be explored here.  Click on the person's name in the list to visualise the scores and hover over the graph for more details.  Select multiple people to overlay their scores for comparison.  The green dotted line is the average score given by the network.



Degree {.tabset}
-----------------------------------------------------------------------



### RQ1

#### 'RQ1' Degree All Scores

```{r}
renderPlotly ({
  fileList[[4]]$degreeAllHistogramList[[1]]
})
```

> The higher the overall degree score, the more tied in the person is to the class.  Those learners who score nearest the average are those who are best placed to develop resiliency in the relational network of the class when they are encouraged to relate to one another, because they have connections to bring to bear, and have relational overhead to be able to develop further relationships without others suffering from divided attention.

#### 'RQ1' Degree In Scores

```{r}
renderPlotly ({
  fileList[[4]]$degreeInHistogramList[[1]]
})
```

> A higher 'Degree in' score indicates that more people in the class come
to this person for information

#### 'RQ1' Degree Out Scores

```{r}
renderPlotly({
  fileList[[4]]$degreeOutHistogramList[[1]]
})
```

> A higher 'Degree out' score indicates that the person is well connected within the class.

